Title Goes Here

### 2020-03-30 analysis/paper/paper.Rmd
Split the chunks

library(here)
```

@@

@@

#Compare multiple artifacts 
#Open multiple tps files 
#This will need to be changed to read files inside the project
datadir <- here("/analysis/data/raw_data/")
files <- dir(datadir, pattern = "*.tps")

@@

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)
library(tidyverse)
df_sitename <- df %>% 
  mutate(files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate(files, into = c("sitename", "files"), sep = "_") %>% 
  select(-files)

#list of all attributes without ID
DF <- df[,1:7]

@@

@@

>>>>

library(here)

library(tidyverse)
```

@@

#Compare multiple artifacts 
#Open multiple tps files. This will need to be changed to read files inside the project
datadir <- here("/analysis/data/raw_data/")
files <- dir(datadir, pattern = "*.tps")
```

```{r}
#attributes of the points by calculating distance between landmakrs

@@

@@

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)

df_sitename <- df %>% 
  mutate(files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate(files, into = c("sitename", "files"), sep = "_") %>% 
  select(-files)

#list of all attributes without ID
DF <- df[,1:7]
```

Correlation, Coefficient or variation, PCA
```{r}
# Correlations with significance levels
library(Hmisc)
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

@@

SYG6 site data and analysis

@@

I'm working on how to read oulines and how to use them for anlaysis

```{r}
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function. 
readalltps = function (file) 
{
    out = list()
    exOut <- FALSE
    noutline <- 0
    input <- readLines(file)
    LM <- grep("LM=", input)
    LMstring <- input[LM]
    nLM <- sapply(LMstring, strsplit, split = "=")
    nLM <- unlist(nLM)
    nLM <- as.integer(nLM[-which(nLM == "LM")])
    nobs <- length(nLM)
    ID <- grep("ID=", input)
    IDstring <- input[ID]
    nID <- sapply(IDstring, function(x) {
        x <- gsub("=", "_", x)
    })
    nID <- gsub(" ", "", unlist(nID))
    out$ID <- nID
    outline <- grep("CURVES=", input)
    if (length(outline) > 0) {
        exOut <- TRUE
        outlinestring <- input[outline]
        noutline <- sapply(outlinestring, strsplit, split = "=")
        noutline <- unlist(noutline)
        noutline <- as.integer(noutline[-which(noutline == "CURVES")])
        LMoutline <- (sapply(outline, function(x) {
            x <- max(which(LM < x))
        }))
    }
    LMdata <- list()
    for (i in 1:nobs) {
        if (nLM[i] > 0) {
            LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
                1):(LM[i] + nLM[i]))]), split = " ")))
            LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
        else LMdata[[i]] <- NA
    }
    names(LMdata) <- nID
    out$LM <- LMdata
    if (exOut) {
        outlineData <- list()
        for (i in 1:nobs) {
            if (i %in% LMoutline) {
                i1 <- grep(i, LMoutline)
                outlinetmp <- list()
                ptr <- outline[i1] + 1
                j <- 1
                while (j <= noutline[i1]) {
                  tmpnr <- as.integer(unlist(strsplit(input[ptr], 
                    split = "="))[2])
                  outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
                    1):(ptr + tmpnr)], split = " "))), tmpnr, 
                    2, byrow = TRUE)
                  ptr <- ptr + tmpnr + 1
                  j <- j + 1
                }
                outlineData[[i]] <- outlinetmp
            }
            else outlineData[[i]] <- NA
        }
        names(outlineData) <- nID
        out$outlines <- outlineData
    }
    cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
    return(out)
}

lm_trial <- readalltps(here("analysis/data/raw_data/A_BG_2.tps"))
